### 2015-03-09 article/article.tex
commit

\section{Tools}
\subsection{MGI}
Mouse Genome Informatics\footnote{\url{http://www.informatics.jax.org/}, \today}.
\subsection{MPD}
Mouse Phenome Database\footnote{\url{http://phenome.jax.org/}, \today}~\cite{mpd}.

>>>>

\section{Tools}
\subsection{MGI}
Mouse Genome Informatics\footnote{\url{http://www.informatics.jax.org/}, \today} is a database for the laboratory mouse, which makes information about integrated genetics and associated phenotypes and alleles available.
The 49 nuclear receptors were searched in the MGI database to achieve an association between these nuclear receptors and phenotypes which arise from alternation in the scope of their genes. 
\subsection{MPD}
Mouse Phenome Database\footnote{\url{http://phenome.jax.org/}, \today}~\cite{mpd}.
